\mytitle{}

### 2018-11-04 paper/paper.tex
Improvements + SPF explained.

\title{\mytitle{}}
\author{
%	Kyle A.\ Simpson\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant number EP/M508056/1].},
%	Dimitrios P.\ Pezaros\\
%	University of Glasgow, Glasgow, Scotland,\\
%	\email{k.simpson.1@research.gla.ac.uk}
Anonymous Giraffe\thanks{This work was supported by a nameless, shapeless funder [grant number 7].},
Anonymous Badger\\
Unnamed Department, Nowhere\\
\email{giraffe.a@unnamed.com}
}

@@

We employ the reward functions introduced by \textcite{DBLP:journals/eaai/MalialisK15}; in particular, we make use of their global reward as a performance metric and their \emph{coordinated team learning} (CTL) reward for training.
These assume the presence of a classifier, $g(\cdot)$, which estimates the volume of `legitimate traffic' received at any point in the network.
At time $t$ an agent $v$ (with team leader $l_v$) receives either $R_{t}^{\mathit{Global}}$ or $R_{t}^{\mathit{CTL}}$:
\begin{subequations}
\newcommand{\cond}[2]{\operatorname{c}_{#1,t}#2}
\newcommand{\load}[1]{\operatorname{load}_{t}(#1)}
\begin{gather}
\cond{f} = [\load{s} > U_s],\\
\cond{c}{(v)} = [\load{l_v} > U_s/k],\\
R_{t}^{\mathit{Global}} = (1 - \cond{f}) \frac{g(\load{s})}{g(\load{\mathit{total}})} - \cond{f},\\
R_{t}^{\mathit{CTL}}(v) = (1 - \cond{f}\cond{c}{(v)}) \frac{g(\load{l_v})}{g(\load{\mathit{team}})} \allowbreak - \cond{f} \cond{c}{(v)},
\end{gather}
where $\load{\mathit{total}}$ and $\load{\mathit{team}}$ refer to the load across all egress points in the network and in $v$'s team, respectively.
\end{subequations}

@@

\begin{figure}
	\includegraphics[width=\linewidth]{../plots/online-varyN-nginx}
	\caption{
		Comparison of preserved traffic across different traffic models, choosing $n=2$ hosts per egress node.
		No actions are taken in the ``baseline'' entries.
		The agents examined here perform above the baseline when traffic sources pay no mind to congestion control, but perform significantly worse for live TCP traffic (nginx).
		\label{fig:nginx-coffin-nail}
	}
\end{figure}

@@

\subsection{Traffic Model}
%?? Legitimate traffic: TCP traffic (HTTP clients downloading web pages, dependent resources and files) with a mixture of lifetimes for each request.
To model legitimate traffic the server node runs an nginx v1.10.3 HTTP daemon, serving statically generated web pages alongside various large files and binaries.
Benign hosts run a simple libcurl-based application written in Rust, repeatedly requesting resources from the server.
This provides two modes of operation:
\begin{itemize}
	\item \emph{long flow} testing has each host constantly request a large binary file, such as a tarball of GCC8;
	\item \emph{request-chain} testing has each host request several random files known to exist within the website, followed by any dependent resources for each (stylesheets, images, etc.). On completion, a host changes its IP to minimise downtime of inbound data while separating statistics per-flow. This presents a more balanced distribution of flow duration and size.
\end{itemize}
Each host's download rate is limited to match whatever maximum bandwidth was assigned to it.

@@

\section{Acting On Individual Sources}

?? High-level overview...

\subsection{Models}

?? Talk about the modifications to standard: multiple actions per-timestep, updating many traces from one reward...

?? Timed Random Sequential flow visitation.

?? Accordingly, reward functions aim to maximise the downstream throughput. Reward function direction for overload + protected loads.

?? Talk about SPF -- Influenced by SPIFFY \cite{DBLP:conf/ndss/KangGS16}. Why? To demonstrate the design of a model which includes some aspects of real-world knowledge, and to see whether making an agent less ``free-form'' might allow us to trade power for learning speed (smaller action space etc.).

@@

%\begin{figure*}
%	\centering
%	\begin{subfigure}{0.32\linewidth}
%		\includegraphics[width=\linewidth]{../plots/ftprep-cap-good}
%	\end{subfigure}
%	\begin{subfigure}{0.32\linewidth}
%		\includegraphics[width=\linewidth]{../plots/ftprep-cap-good-2}
%	\end{subfigure}
%	\begin{subfigure}{0.32\linewidth}
%		\includegraphics[width=\linewidth]{../plots/ftprep-cap-good-2}
%	\end{subfigure}
%	\caption{
%		Features: how good are they really? These are for UDP. As you can see, Most things are pretty average (except for \emph{Mean IAT}, which dominates).
%		\label{fig:udp-cap-feature-plots}
%	}
%\end{figure*}

@@

\begin{figure*}
	\begin{subfigure}{0.32\linewidth}
		\includegraphics[width=\linewidth]{../plots/ftprep-tcp-cap-good}
	\end{subfigure}
	\begin{subfigure}{0.32\linewidth}
		\includegraphics[width=\linewidth]{../plots/ftprep-tcp-cap-good-2}
	\end{subfigure}
	\begin{subfigure}{0.32\linewidth}
		\includegraphics[width=\linewidth]{../plots/ftprep-tcp-cap-good-2}
	\end{subfigure}

@@

?? NEED TO SAY SOMEWHERE: Baselines use TC for establishing interleaving/buffers filling etc., when MARL+ or SPF are in play then disabling TC (thus allowing illegal states, with \num{-1} reward marking them as such---``negative reinforcement'') may accelerate learning. We have a choice---but the results show that for TCP we WANT TC enabled...

@@

>>>>

\title{\mytitle{}}
\author{
%	Kyle A.\ Simpson\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant number EP/M508056/1].},
%	Dimitrios P.\ Pezaros\\
%	University of Glasgow, Glasgow, Scotland,\\
%	\email{k.simpson.1@research.gla.ac.uk}
Anonymous Giraffe\thanks{This work was supported by a nameless funder [grant number 7].},
Anonymous Badger\\
Unnamed Department, Nowhere\\
\email{giraffe.a@unnamed.com}
}

@@

We employ the reward functions introduced by \textcite{DBLP:journals/eaai/MalialisK15}; in particular, we make use of their global reward as a performance metric and their \emph{coordinated team learning} (CTL) reward for training.
These assume the presence of a classifier, $g(\cdot)$, which estimates the volume of `legitimate traffic' received at any point in the network.
At time $t$ an agent $v$ (with team leader $l_v$) receives either $R_{t}^{\mathit{Global}}$ or $R_{t}^{\mathit{CTL}}$:
\begin{subequations}
\newcommand{\cond}[2]{\operatorname{c}_{#1,t}#2}
\newcommand{\load}[1]{\operatorname{load}_{t}(#1)}
\begin{gather}
\cond{f} = [\load{s} > U_s],\\
\cond{c}{(v)} = [\load{l_v} > U_s/k],\\
R_{t}^{\mathit{Global}} = (1 - \cond{f}) \frac{g(\load{s})}{g(\load{\mathit{total}})} - \cond{f},\label{eqn:reward-rt}\\
R_{t}^{\mathit{CTL}}(v) = (1 - \cond{f}\cond{c}{(v)}) \frac{g(\load{l_v})}{g(\load{\mathit{team}})} \allowbreak - \cond{f} \cond{c}{(v)},\label{eqn:reward-rctl}
\end{gather}
where $\load{\mathit{total}}$ and $\load{\mathit{team}}$ refer to the load across all egress points in the network and in $v$'s team, respectively.\label{eqn:reward}
\end{subequations}

@@

\begin{figure}
	\includegraphics[width=\linewidth]{../plots/online-varyN-nginx}
	\caption{
		Comparison of preserved traffic across different traffic models, choosing $n=2$ hosts per egress node.
		No actions are taken in the ``baseline'' entries.
		The agents examined here perform above the baseline in all cases, but perform significantly worse for live TCP traffic (nginx).
		\label{fig:nginx-coffin-nail}
	}
\end{figure}

@@

\subsection{Traffic Model}
%?? Legitimate traffic: TCP traffic (HTTP clients downloading web pages, dependent resources and files) with a mixture of lifetimes for each request.
To model legitimate traffic the server node runs an nginx v1.10.3 HTTP daemon, serving statically generated web pages alongside various large files and binaries.
Benign hosts run a simple libcurl-based application written in Rust, repeatedly requesting resources from the server.
Each host's download rate is limited to match whatever maximum bandwidth was assigned to it.
This provides two modes of operation:
\begin{itemize}
	\item \emph{long flow} testing has each host constantly request a large binary file, such as a tarball of GCC8;
	\item \emph{request-chain} testing has each host request several random files known to exist within the website, followed by any dependent resources for each (stylesheets, images, etc.). On completion, a host changes its IP to minimise downtime of inbound data while separating statistics per-flow. This presents a more balanced distribution of flow duration and size.
\end{itemize}

@@

\section{Acting On Individual Sources}
Our main hypothesis is that the best method for advancing past the current shortcomings of RL-based DDoS mitigation is to modify the design of agents such that filtering decisions are computed per source.
However, any of these alterations must account for computational constraints imposed by the deployment environment---the amount of flows passing over an agent is unbounded.
We describe and justify our enhancements to the RL model of \textcite{DBLP:journals/eaai/MalialisK15}, present a new model which draws on domain knowledge leveraged by SPIFFY \cite{DBLP:conf/ndss/KangGS16}, and offer an empirical investigation into the effectiveness of flow-level statistics on live decision-making.

\subsection{Marl++}\label{sec:marl-plus}
%\fakepara{Multiple actions}
%?? Talk about the modifications to standard: multiple actions per-timestep, updating many traces from one reward...
Modifying the frequency with which actions and value functions are updated has important consequences for not only overall system performance, but also in \emph{how} an agent learns.
We choose to adapt these algorithms to prioritise rapid response to changes in network state and to visit as many state-to-state transitions as possible to facilitate effective learning.
To this end, we allow agents to make many decisions per timestep.
We maintain the last state-action pair associated with each source IP, and calculate any actions for the flows which still exist.
Finally, we update $\wvec{}$ according to \cref{eqn:sg-sarsa} with each available trace and the sole reward measurement an agent has at that time.
As exploration still occurs for each action, this approach reduces $\epsilon$ multiple steps for each $t$.
In turn, we increase the annealing window for $\epsilon$ to \num{8000} action choices to preserve exploration over time, while accounting for the greater volume of decisions being made.

%\fakepara{Timed Random Sequential actions}
Taking actions in this manner means that any agents are assigned a larger, and potentially unbounded, set of tasks to perform every time they receive load and flow statistics from the network and their parent switch.
This introduces numerous potential issues: inability to response to unexpected changes in flow state, delayed service of new flows and risks that flow states become outdated; at their worst, these present additional attack surface to an adversary.
To adapt to these problems, we make use of \emph{timed random sequential} updates.
Each agent begins with an empty work list.
For the set of flows active in any timestep, we shuffle the list and perform as many action calculations and updates as possible, within a set time limit.
Uncompleted work is passed on to the next timestep, until it is emptied, at which point is is repopulated using the set of available measurements.
To ensure that flow control actions are made with recent information, we combine state vectors for unvisited flows in the current work set, and replace the stored vector for all others.
State vector combination is done by summing deltas and packet counts, updating means via weighted sums, and replacing all other fields with the newest measurements.
Following \textcite{DBLP:conf/sigcomm/ChenL0L18}'s observations concerning short flows, we maintain a deadline of \SI{1}{\milli\second}---in tests, an agent is typically able to process around 8 flows in this time.
We expect this should be tuned based on the frequency at which statistics arrive.
%?? Prune old? We can get through 8 per iteration, might use this as a basis for knowing when to say ``enough is enough''.

{
\newcommand{\load}[2]{\operatorname{load}^{#2}_{t}(#1)}
\newcommand{\uload}[1]{\load{#1}{\uparrow}}
\newcommand{\dload}[1]{\load{#1}{\downarrow}}
\newcommand{\bload}[1]{\load{#1}{\updownarrow}}
\newcommand{\cond}[2]{\operatorname{c}_{#1,t}#2}
%\fakepara{Reward function directionality}
The reward functions, as defined, do not take traffic direction into account.
We redefine these to identify overload states using both upstream and downstream loads, while allowing customisation of which direction is chosen for protection.
Denoting the upstream, downstream and combined loads $\uload{s}, \dload{s}, \bload{s}$, we modify \cref{eqn:reward}:
\begin{subequations}
\begin{gather}
\cond{f} = [\max(\uload{s}, \dload{s}) > U_s],\\
\cond{c}{(v)} = [\max(\uload{l_v}, \dload{l_v}) > U_s/k],
\end{gather}
\end{subequations}
replacing $\load{t}{}$ in \crefrange{eqn:reward-rt}{eqn:reward-rctl} with whichever directional load is prioritised.
We choose $\uload{\cdot}$ for our UDP-based models and $\dload{\cdot}$ for HTTP, though we expect that $\bload{\cdot}$ would be the most suitable for general deployment or heterogeneous traffic patterns.
}

\subsection{SPF: SPIFFY Lite}

An important question to ask while exploring the design space of RL agents is whether (and how) domain knowledge can improve the performance or learning rate of a defence system.
This often comes as a trade-off: expressive power and unfettered control, weighed against the smaller action spaces afforded by existing insight or structure.
We present a second model, relying on the measurements of \textcite{DBLP:conf/ndss/KangGS16} which suggest that bot attack flows cannot scale up to match an increase in available bandwidth.
While it is not stated whether this behaviour applies to amplification attacks, we expect this to remain the case; the upload rate of any amplifier will be fixed at its upper bound given that upstream links of bots are saturated.
Moreover, bots receive no feedback on the effective throughput of their attack flows.

How might we apply their observations within the RL paradigm, while tailoring them towards non-ISP deployment?
Our approach is to model how an agent treats each flow using a simple finite state automaton: we restrict $p \in \left\{ 0.00, 0.05, 0.25, 0.50, 1.0 \right\}$, reducing the action set to \emph{maintain}, \emph{increase}, or \emph{decrease} $p$ in single steps.
To enable temporary bandwidth expansion in resource constrained deployments, every flow is initially placed under light packet drop ($p=0.05$, or state 1), corresponding to roughly a \SI{50}{\percent} rate reduction for TCP flows in our test topology.
This uneven spread of choices for $p$ allows light and heavy rate reduction to be applied to both congestion-aware and non-congestion-aware traffic as required.
We combine this with the enhancements described in \cref{sec:marl-plus}.
%?? Talk about SPF -- Influenced by SPIFFY \cite{DBLP:conf/ndss/KangGS16}. Why? To demonstrate the design of a model which includes some aspects of real-world knowledge, and to see whether making an agent less ``free-form'' might allow us to trade power for learning speed (smaller action space etc.). Also, because we might be able to use its insights in an environ where we don't have spare bandwidth? Such a model means we need an agents need to ``plan ahead'', i.e. have $\gamma \ne 0$. We found $\gamma = 0.8$ to be the most effective choice. We also use most of the techniques from above.

This model is significantly different from the perspective of RL parameter tuning: each agent now requires the capability to plan ahead, since they may no longer choose $p$ directly from any state.
This entails choosing some discount factor $\gamma \ne 0$, allowing the value of future states to influence state-action value updates.
We found $\gamma = 0.8$ to be the most effective choice during exploratory testing.

@@

%\begin{figure*}
%	\centering
%	\begin{subfigure}{0.32\linewidth}
%		\includegraphics[width=\linewidth]{../plots/ftprep-cap-good}
%	\end{subfigure}
%	\begin{subfigure}{0.32\linewidth}
%		\includegraphics[width=\linewidth]{../plots/ftprep-cap-good-2}
%	\end{subfigure}
%	\begin{subfigure}{0.32\linewidth}
%		\includegraphics[width=\linewidth]{../plots/ftprep-cap-good-3}
%	\end{subfigure}
%	\caption{
%		Features: how good are they really? These are for UDP, but capped. As you can see, Most things are pretty average (except for \emph{Mean IAT}, which dominates).
%		\label{fig:udp-cap-feature-plots}
%	}
%\end{figure*}

@@

\begin{figure*}
	\begin{subfigure}{0.32\linewidth}
		\includegraphics[width=\linewidth]{../plots/ftprep-tcp-cap-good}
	\end{subfigure}
	\begin{subfigure}{0.32\linewidth}
		\includegraphics[width=\linewidth]{../plots/ftprep-tcp-cap-good-2}
	\end{subfigure}
	\begin{subfigure}{0.32\linewidth}
		\includegraphics[width=\linewidth]{../plots/ftprep-tcp-cap-good-3}
	\end{subfigure}

@@

?? NEED TO SAY SOMEWHERE: Baselines use TC for establishing interleaving/buffers filling etc., when MARL+ or SPF are in play then disabling TC (thus allowing illegal states, with \num{-1} reward marking them as such---``negative reinforcement'') may accelerate learning. We have a choice---but the results show that for TCP we WANT TC enabled... For UDP, we actually get a slight degradation in performance. This suggests a kind of ``banding'', perhaps?

@@

?? What if there are too many flows and a decision set is never completed? Uh... trap door and skip to next set after 50 flow decisions or something?
